---
title: "Initial Korean covid 19"
author: "Chris Gonzalez"
date: "June 21,2023"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
options(digits=2)
require(tidyverse)
require(tigerstats)
require(lubridate)
kRdata <- read.csv(file = 'kRdata.csv')
kRdata <- kRdata %>%
mutate(across(where(is.character), as.factor))

```
### Data is from the Patient_Info dataset from South Korea 1 Jan to 1 May 2020
### This data was retrieved from a downloadable zip file from kaggle

Some of the data was uncoded for sex - sex must be just male or female
77 of the data entries were coded sex  as blank, so we omit these.
state of a patient must be died or alive - we adjust that as well   
  
# Your Question - Is dying independent of sex?

## Methods 
The present study aims to conduct an analysis of patients, taking into consideration the variable factor of Sex and its result factor variable. To facilitate the examination of the data and initiate the analysis, a graphical representation will be generated using the ggplot package. Additionally, both numerical and inferential techniques will be employed to further explore and interpret the findings. This will help determine if sex had any impact in the decease. 



## Graphical results - use ggplot commands to do this  

```{r}
dd2 <- kRdata %>% group_by(result,Sex) %>% summarize(count=n()) %>% mutate(prcnt=count/sum(count))


# the group_by followed by summarize(count=n())

basicC <- ggplot(dd2,aes(x=result,y=count,fill=Sex))
basicC + geom_bar(stat="identity",position="dodge")

#Now for percentage plot

basicCC <- ggplot(dd2,aes(x=result,y=prcnt*100,fill=Sex)) 
basicCC + geom_bar(stat="identity", position = "dodge")
```
  
Based on the chart analysis, it is evident that the female population outnumbers the male population. Upon closer examination of the death rate data, it is estimated that males comprise approximately 65% of the fatalities. The box plot further reinforces this observation by illustrating a disproportionately higher percentage of male individuals succumbing to COVID-19.




  
## Numerical results

```{r}
table2 <- xtabs(~result + Sex, data=kRdata)
rowPerc(table2)
colPerc(table2)
```
According to the numerical data, the study indicates that 56% of females and 44% of males have survived. Furthermore, it reveals that 36% of females and 64% of males have succumbed to the condition. In terms of mortality, the male deaths exhibit a dominant proportion. In the second result it show 98.7% female adn 97% are males that are alive, and out of thes 1.4% females have died and 3% of males have died.


## Inferential results 






## Conclusions

